\textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification}

### 2025-01-17 paper/main.tex
edit conclusion -> future work outro

\texttt{ZKLoRA} provides a fast, robust mechanism to ensure that private LoRA modules remain consistent with a large base model. Our evaluations indicate that each LoRA module’s correctness can be verified in about 1--2 seconds, even for multi-billion-parameter LLMs. This efficiency bridges the gap between privacy-preserving LoRA development and practical, real-time validation in large-scale deployments. Future expansions could integrate multi-contributor LoRAs, advanced zero-knowledge proofs for further performance gains, or partial data-privacy frameworks to shield user inputs as well as LoRA parameters.

>>>>

\texttt{ZKLoRA} provides a fast, robust mechanism to ensure that private LoRA modules remain consistent with a large base model. Our evaluations indicate that each LoRA module’s correctness can be verified in less than 2 seconds, even for multi-billion-parameter LLMs. This efficiency bridges the gap between privacy-preserving LoRA development and practical, real-time validation in large-scale deployments. In terms of future work, the most relevant and immediate work would be adding polynomial commitments of the base model's activations (those that are sent as input to the LoRA contributor). This would take us one step closer to providing end-to-end verifiability of inference computation for LoRA-finetuned models.  Other avenues of expansion could be integrating multi-contributor LoRAs, advanced zero-knowledge proofs for further performance gains, or partial data-privacy frameworks to shield user inputs as well as LoRA parameters.
